Argennon: A Scalable Smart Contract Platform

### 2021-07-01 tex/sections/incentive.tex
Fix a typo
Signed-off-by: aybehrouz <behrouz_ayati@yahoo.com>

\subsection{Stashing}\label{subsec:stashing}

@@

Only behaviours will be stashed that can not happen due to a mistake or an attack. These behaviours include:
\begin{itemize}
    \item Signing a certificate for a block that is not conditionally valid.
    \item Signing a certificate for two different blocks at the same height if none of them
    is a fork block or a seal block.\footnote{signing
    a fork block and a normal block at the same height usually is a malicious behaviour. However, it will not be
    stashed because there are circumstances that a honest user could mistakenly do that.}
\end{itemize}

>>>>

\subsection{Penalties}\label{subsec:penalties}

@@

Only behaviours will be punished that can not happen due to a mistake or an attack. These behaviours include:
\begin{itemize}
    \item Signing a certificate for a block that is not conditionally valid.
    \item Signing a certificate for two different blocks at the same height if none of them
    is a fork block or a seal block.\footnote{signing
    a fork block and a normal block at the same height usually is a malicious behaviour. However, it will not be
    penalized because there are circumstances that a honest user could mistakenly do that.}
\end{itemize}
